You are the way you structurally talk: Structural-temporal neighborhoods of posts to characterize users in online forums

### 2016-03-29 doc/paper.tex
neighborhoods bt order and time

In order to detect more complex types of neighborhoods we enlarge the spatial radius to $r=4$. Figure~\ref{fig:neighborhoods_4_4} shows the eight detected neighbors and their frequency. It is interesting to see different structures like chains or stars where the root node migh or might no appear and the ego post is placed at different positions.

@@

\section{Conclusions}
\bibliographystyle{spbasic} 
%\bibliographystyle{chicago} 
%\bibliographystyle{plainnat} 
\bibliography{library}
\end{document}

>>>>

In order to detect more complex types of neighborhoods we enlarge the spatial radius to $r=4$. Figure~\ref{fig:neighborhoods_4_4} shows the eight detected neighbors and their frequency. It is interesting to see different structures like chains or stars where the root node might or might no appear and the ego post is placed at different positions.

@@

\section{Conclusions}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIX
%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\noindent \textbf{\Large Appendix}
\vspace{-0.1cm}

\begin{align}
p(\Delta t_k | \Delta t_1,...\Delta t_{k-1})
&=
\int p(\Delta t_k | \lambda_{k-1})
p(\lambda_{k-1} |\Delta t_1,...\Delta t_{k-1})\\
&=\frac{(\beta + n\overline{x})^{\alpha+n}}{(\beta + n\overline{x}+\Delta t_k)^{\alpha+n+1}}(\alpha+n)
\end{align}
First we work on the posterior distribution over $\lambda_{k-1}$:
\begin{align}
p(\lambda_{k-1} |\Delta t_1,...\Delta t_{k-1})
&\propto
p(\Delta t_1,...\Delta t_{k-1} | \lambda_{k-1} |)p(\lambda_{k-1})\\
&\propto 
\prod \lambda e^{-\lambda x}  \lambda^{\alpha-1}e^{-\beta \lambda}\\
&\propto
\lambda^{\alpha+k-1}
e^{-(\beta+k\overline{x})\lambda}\\
&\propto\mathcal{G}(\alpha+k, \beta + n\overline{x})
\end{align}

And then the predictive posterior is:
\begin{align}
p(\Delta t_k | \Delta t_1,...\Delta t_{k-1})&=
\int
p(\Delta t_k | \lambda_{k-1})
\mathcal{G}(\lambda_{k-1} | \alpha+k, \beta + n\overline{x})\\
&=
\frac{(\beta+n\overline{x})^{\alpha+k}}{\Gamma(\alpha+k)}
\int
\lambda e^{-\lambda \Delta_k}
\lambda^{\alpha+k-1}
e^{-(\beta+n\overline{x})\lambda}
\text{d}\lambda\\
&=
\frac{(\beta+n\overline{x})^{\alpha+k}}{\Gamma(\alpha+k)}
\int
\lambda^{(\alpha+k+1)-1}
e^{-(\beta+n\overline{x}+\Delta_k)\lambda}
\text{d}\lambda\\
&=
\frac{(\beta+n\overline{x})^{\alpha+k}}{\Gamma(\alpha+k)}
\frac{\Gamma(\alpha+k+1)}{(\beta+n\overline{x}+\Delta_k)^{\alpha+k+1}}\\
&=
\frac
{(\beta+n\overline{x})^{\alpha+k}}{(\beta+n\overline{x}+\Delta_k)^{\alpha+k+1}}
(\alpha+k)
\end{align}

\bibliographystyle{spbasic} 
%\bibliographystyle{chicago} 
%\bibliographystyle{plainnat} 
\bibliography{library}
\end{document}
